---
title: "Demographics in Site16 Participants"
output: html_notebook
---
Just load the text files, because the .Rds file is too huge for Release 2.0 and my computer.

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(summarytools)
library(PerformanceAnalytics)
library(stringr)
data_dir='~/Documents/projects/in_progress/spatial_topography_parcellations_ABCD/data/subjData/Release2/'
output_data_dir='~/Documents/projects/in_progress/spatial_topography_parcellations_ABCD/data/subjData/Release2_fixed/'
sites <- read.delim(paste0(data_dir,"abcd_lt01.txt"))
sites = sites[-1,]
sites = droplevels(sites)
sites <- select(sites, -c(collection_id:dataset_id))
sites$subjectid <- sites$subjectkey
socio <- read.delim(paste0(data_dir,"acspsw03.txt"))
socio = socio[-1,]
socio = droplevels(socio)
socio <- select(socio, -c(collection_id:dataset_id))
socio$subjectid <- socio$subjectkey
income <- read.delim(paste0(data_dir,"pdem02.txt")) #this was accidentally the longitudinal demographics survey, use the general one called pdem02 instead
income = income[-1,]
income = droplevels(income)
income <- select(income, -c(collection_id:dataset_id))
income$subjectid <- income$subjectkey
yksads <- read.delim(paste0(data_dir,"abcd_ptsd01.txt"))
yksads = yksads[-1,]
yksads = droplevels(yksads)
yksads <- select(yksads, -c(collection_id:dataset_id))
yksads$subjectid <- yksads$subjectkey
#get hormones
hormoneqs <- read.delim(paste0(data_dir,"sph01.txt"))
hormoneqs = hormoneqs[-1,]
hormoneqs = droplevels(hormoneqs)
hormoneqs <- select(hormoneqs, -c(collection_id:dataset_id))
hormoneqs$subjectid <- hormoneqs$subjectkey
hormoneqs$eventname <- hormoneqs$visit
hormonedhea <- read.delim(paste0(data_dir,"abcd_hsss01.txt"))
hormonedhea = hormonedhea[-1,]
hormonedhea = droplevels(hormonedhea)
hormonedhea <- select(hormonedhea, -c(collection_id:dataset_id))
hormonedhea$subjectid <- hormonedhea$subjectkey
main<- left_join(sites,socio, by=c("subjectid", "eventname"))
main <- left_join(main, income, by=c("subjectid", "eventname"))
main <- left_join(main, yksads, by=c("subjectid", "eventname"))
main <- left_join(main, hormoneqs, by=c("subjectid", "eventname"))
main <- left_join(main, hormonedhea, by=c("subjectid", "eventname"))
```

#Initial demographic analyses in site16
```{r demographics in n698, echo=FALSE}
subjlist_dir='/Users/utooley/Documents/projects/in_progress/spatial_topography_parcellations_ABCD/data/subjLists/release2/site16/'
main <- filter(main, eventname=="baseline_year_1_arm_1") %>% filter(.,site_id_l=="site16") #filter out only the baseline visits
subjlist <- read.table(paste0(subjlist_dir, "n698_release2_site16_0.2mm_bids.txt"), col.names = c("subjectid"))
main$subjectid <- str_remove(main$subjectid, "_") #subjectid has a _ in it after NDAR in the NDAR data, doesn't match subject list
main <- left_join(subjlist, main, by="subjectid")
main$ageyrs <- as.numeric(as.character(main$interview_age.y))/12
summary(main$ageyrs)
freq(main$gender.x)
freq(main$race_ethnicity) #1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other
freq(main$demo_comb_income_v2_l) #income as a factor
```

# Demographics for the other two sites
For when we want to look at QC metrics or motion on a scan-by-scan basis.
```{r demographics for other two sites, echo=FALSE}
subjlist_dir='/Users/utooley/Documents/projects/in_progress/spatial_topography_parcellations_ABCD/data/subjLists/release2/site14site20/'
main <- filter(main, eventname=="baseline_year_1_arm_1") %>% filter(.,site_id_l=="site14" | site_id_l=="site20") #filter out only the baseline visits
subjlist <- read.table(paste0(subjlist_dir, "n611_release2_site14site20_0.2mm.txt"), col.names = c("subjectid"))
main$subjectid <- str_remove(main$subjectid, "_") #subjectid has a _ in it after NDAR in the NDAR data, doesn't match subject list
subjlist$subjectid <- str_remove(subjlist$subjectid, "sub-") #subjectlisthas a sub- before it
main <- left_join(subjlist, main, by="subjectid")
main$ageyrs <- as.numeric(as.character(main$interview_age.y))/12
summary(main$ageyrs)
freq(main$gender.x)
freq(main$race_ethnicity) #1 = White; 2 = Black; 3 = Hispanic; 4 = Asian; 5 = Other
freq(main$demo_comb_income_v2_l) #income as a factor
```
# procfmri <- read.delim(paste0(nda_data_dir,"fmriresults01.txt"))
# procfmri = procfmri[-1,]
# procfmri = droplevels(procfmri)
# procfmri <- select(procfmri, -c(collection_id:subjectkey))
# procfmri$subjectid <- procfmri$src_subject_id
#mriqc1 <- read.delim(paste0(data_dir,"mriqc02.txt"))
# mriqc1 = mriqc1[-1,]
# mriqc1 = droplevels(mriqc1)
# mriqc1 <- select(mriqc1, -c(collection_id:subjectkey))
# mriqc1$subjectid <- mriqc1$src_subject_id
# mriqc2 <- read.delim(paste0(data_dir,"mriqcp202.txt"))
# mriqc2 = mriqc2[-1,]
# mriqc2 = droplevels(mriqc2)
# mriqc2 <- select(mriqc2, -c(collection_id:subjectkey))
# mriqc2$subjectid <- mriqc2$src_subject_id
# fsqc <- read.delim(paste0(data_dir,"freesqc01.txt"))
# fsqc = fsqc[-1,]
# fsqc = droplevels(fsqc)
# fsqc <- select(fsqc, -c(collection_id:subjectkey))
# fsqc$subjectid <- fsqc$src_subject_id
# betnet <- read.delim(paste0(data_dir,"abcd_betnet02.txt"))
# betnet = betnet[-1,]
# betnet = droplevels(betnet)
# betnet <- select(betnet, -c(collection_id:subjectkey))
# betnet$subjectid <- betnet$src_subject_id
# sites <- read.delim(paste0(data_dir,"abcd_lt01.txt"))
# sites = sites[-1,]
# sites = droplevels(sites)
# sites <- select(sites, -c(collection_id:subjectkey))
# sites$subjectid <- sites$src_subject_id
# sites <- read.delim(paste0(data_dir,"abcd_lt01.txt"))
# sites = sites[-1,]
# sites = droplevels(sites)
# sites <- select(sites, -c(collection_id:subjectkey))
# sites$subjectid <- sites$src_subject_id
#main<- right_join(procfmri,main, by="subjectid")
# main<- left_join(main,mriqc2, by="subjectid")
# main<- left_join(main,fsqc, by="subjectid")
# main<- left_join(main,betnet, by="subjectid")
# main<- left_join(main,sites, by="subjectid")
```